\vspace{-15mm}\fontsize{24pt}{10pt}\selectfont\textbf{// All comments are NOT created equal}

### 2014-12-05 Proposal.tex
somewhat final version?

\documentclass[twoside, 12pt]{article}
\usepackage{amsmath}
\usepackage{lipsum} % Package to generate dummy text throughout this template
\usepackage[english]{isodate}% http://ctan.org/pkg/isodate
\usepackage{pgfgantt}
\usepackage[show]{ed}
\setlength{\parindent}{0pt}
\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.2} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage{minted}
\usepackage[section]{placeins}
\usepackage{nameref}
\usemintedstyle{autumn}
\usepackage[hmarginratio=1:1,top=32mm,left=25mm,right=25mm,columnsep=18pt,bottom=27mm]{geometry} % Document margins
\usepackage{multicol} % Used for the two-column layout of the document
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
\usepackage{hyperref} % For hyperlinks in the PDF
\usepackage{xspace}
\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
\usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them
\usepackage{etoolbox}
\usepackage{eurosym}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

@@

\begin{wrapfigure}{l}{0.6\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.58\textwidth]{assets/Annie4xml3}
    }
  \end{center}
\vspace{-20pt}
  \caption{Narrative Layers and semantic closeness}
  \label{fig:Annie-semantic-closeness}
\vspace{-10pt}
\end{wrapfigure}

@@

\begin{figure}[H]
        \centering
		    \fbox{\includegraphics[width=0.65\textwidth]{assets/Annie4size}}
  \caption{Relative size and relations} 
  \label{fig:Annie-relsize}
\end{figure}

@@

Within knowledge representation, five evaluation criteria for knowledge representation are known \cite{Kohlhase:Complog:base}: Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness. Primitives are the different elements of representation. In terms of evaluation it is important to have intuitive primitive elements. \\

Visual and normal tree-like graph language have different primitives and it is interesting how one can be mapped to the another. When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes. Additionally we can add semantic primitives like attributes to the concepts and to the relations. In normal graphs a relation between two nodes is often quite simple there is one node that is the subject, one node that acts as an object, and the relation that acts like a predicate. Thus we can, for instance, express that the Pythagorean Theorem depends on information about right angles. These structural primitives and semantic primitives provide the basics that graphs can be built on.\\

@@

Since Impress.js provides us with different representation options as outlined in section \ref{sec:inforep}, we can make use of relative size and visual closeness to additionally convey importance, relatedness, and even accessibility of information. Additionally, the connections between different frames do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another. As such the temporal associations show the path that a normal lecture would take. The dependencies that are visualized around each frame allow for the interactiveness.\\

The exact layout of the frames and the best visualization of the relation between the frames is to be determined. Ideally the added expressiveness should lead to Annie having the information about the Pythagorean theorem on a slide-like structure while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily. \\

@@

In this research we will use this knowledge to form an interconnected web of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge. For Annie this means that she would be presented with the information about the Pythagorean theorem in a way that the \textit{course-ancient} and \textit{course-old} information this \textit{course-new} information depends on would be visually close and visually connected. It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in a click.\\

@@

A stretch goal of this project is to have this research accessible for common users that could use it to create their own presentations. Another stretch goal is for \sys to create or change presentations on the fly as outlined in \ref{sec:wp4}. It is not the goal of this research that users should be able to reconstruct the original information graph from the presentation.\\

\section{Timeline}
\label{sec:timeline}

>>>>

\documentclass[twoside, 12pt]{article}
\usepackage{amsmath}
\usepackage{lipsum} % Package to generate dummy text throughout this template
\usepackage[english]{isodate}% http://ctan.org/pkg/isodate
\usepackage{pgfgantt}
%\usepackage[show]{ed}
\setlength{\parindent}{0pt}
\usepackage[sc]{mathpazo} % Use the Palatino font
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\linespread{1.2} % Line spacing - Palatino needs more space between lines
\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage{minted}
\usepackage[section]{placeins}
\usepackage{nameref}
\usemintedstyle{autumn}
\usepackage[hmarginratio=1:1,top=32mm,left=25mm,right=25mm,columnsep=18pt,bottom=27mm]{geometry} % Document margins
\usepackage{multicol} % Used for the two-column layout of the document
\usepackage[hang, small,labelfont=bf,up,textfont=it,up]{caption} % Custom captions under/above floats in tables or figures
\usepackage{booktabs} % Horizontal rules in tables
\usepackage{float} % Required for tables and figures in the multi-column environment - they need to be placed in specific locations with the [H] (e.g. \begin{table}[H])
\usepackage{hyperref} % For hyperlinks in the PDF
\usepackage{xspace}
\usepackage{lettrine} % The lettrine is the first enlarged letter at the beginning of the text
\usepackage{paralist} % Used for the compactitem environment which makes bullet points with less space between them
\usepackage{etoolbox}
\usepackage{eurosym}
\patchcmd{\thebibliography}{\section*{\refname}}{}{}{}
\usepackage{abstract} % Allows abstract customization
\renewcommand{\abstractnamefont}{\normalfont\bfseries} % Set the "Abstract" text to bold
\renewcommand{\abstracttextfont}{\normalfont\small\itshape} % Set the abstract itself to small italic text

@@

\begin{wrapfigure}{l}{0.5\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.48\textwidth]{assets/Annie4xml3}
    }
  \end{center}
\vspace{-20pt}
  \caption{Narrative Layers and semantic closeness}
  \label{fig:Annie-semantic-closeness}
\vspace{-10pt}
\end{wrapfigure}

@@

\begin{figure}[H]
        \centering
		    \fbox{\includegraphics[width=0.6\textwidth]{assets/Annie4size}}
  \caption{Relative size and relations} 
  \label{fig:Annie-relsize}
\end{figure}

@@

Within knowledge representation, five evaluation criteria for knowledge representation are known \cite{Kohlhase:Complog:base}: Expressive Adequacy, Reasoning Efficiency, Primitives, Meta-representation, and Incompleteness. Primitives are the different elements of representation. In terms of evaluation it is important to have intuitive primitive elements. The primitive elements can be further subdivided into structural and semantic primitives \cite{DBLP:dblp_conf/acl/Salveter80}. The structural primitives have little inherent semantics associated with them whereas the semantic primitives carry meaning.\\

Visual and normal tree-like graph language have different primitives and it is interesting how one can be mapped to the other. When we consider tree-like graphs, there are two structural primitives, namely the nodes, which represent concepts, and the edges, which represent relations between nodes. Additionally we can add semantic primitives like attributes to the concepts and to the relations to show what kind of a relation it is. In normal graphs a relation between two nodes is often quite simple: there is one node that acts as the subject, one node that acts as an object, and the relation that acts like a predicate. Thus we can, for instance, express that the Pythagorean Theorem depends on information about right angles (similar to figure \ref{fig:Annie-context}). These structural primitives and semantic primitives provide the basics that graphs can be built on.\\

@@

Since Impress.js provides us with different representation options as outlined in section \ref{sec:inforep}, we can make use of relative size and visual closeness to additionally convey importance, relatedness, and even accessibility of information. Additionally, the connections between different frames do not just connect content that depends on one another but also content that has a temporal connection, similar to slides following one after another. As such the temporal associations show the path that a normal lecture would take. The dependencies that are visualized around each frame allow for interactiveness.\\

The exact layout of the frames and the best visualization of the relation between the frames is to be determined but figure \ref{fig:Annie-relsize} can be seen as a first draft. Ideally the added expressiveness that Impress.js offers should lead to Annie having the information about the Pythagorean theorem on a slide-like structure while having all the information the Pythagorean theorem depends on easily accessible so that she can reach \textit{course-old} information easily. \\

@@

\begin{wrapfigure}{l}{0.4\textwidth}
\vspace{-26pt}
  \begin{center}
  \fbox{
    \includegraphics[width=0.35\textwidth]{assets/Annie3spatial}
    }
  \end{center}
\vspace{-20pt}
  \caption{Guided spatial tour}
  \label{fig:Annie-guided}
\vspace{-10pt}
\end{wrapfigure}

In this research we will use this knowledge to form an interconnected web of information that tells a visual story based on semantic closeness to facilitate the transfer of knowledge. For Annie this means that she would be presented with the information about the Pythagorean theorem in a way that the \textit{course-ancient} and \textit{course-old} information this \textit{course-new} information depends on would be visually close and visually connected (see figure \ref{fig:Annie-guided}). It also means that Annie's teacher can answer Annie's questions easily by just going to the related \textit{course-ancient} information in a click.\\

@@

A stretch goal of this project is to have this research accessible for common users that could use it to create their own presentations. Another stretch goal is for \sys to create or change presentations on the fly as outlined in \ref{sec:wp4}. It is not the goal of this research that users should be able to reconstruct the original information graph from the presentation.\\
\newpage
\section{Timeline}
\label{sec:timeline}
